Manuscript

### 2018-11-09 manuscript.Rmd

## Pearson correlation by lineage
```{r}
PearsonByLineage <- function(lin, dataset) {
  use_data <- filter(dataset, group_general_lineage_name == lin)
  use_data <- filter(use_data, !is.na(RPKM))
  use_data_summ <- use_data %>% count(Drug_Gene)
  use_data_summ <- filter(use_data_summ, n >= 3)
  use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
  if(nrow(use_data_filt) > 0) {
    pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
    pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
    pearson_res$group_general_lineage_name <- lin
    return(pearson_res)
  }
}
```

@@

  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Gene-drug association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage, margin = list(t = 75, l = 75), xaxis5 = list(title = "Pearson correlation coefficient between gene-drug AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

@@

## Make per-drug boxplots
```{r}
makeDrugBoxplots <- function(drug, dataset) {
  if(dataset == "CCLE" | dataset == "ccle") {
    use_data <- filter(ccle_data_g2p_genesfilt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ccle_signif_g2p_ByDrug[[drug]]
    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
  }
  else if(dataset == "CTRP" | dataset == "ctrp") {
    use_data <- filter(ctrp_data_g2p_genesfilt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ctrp_signif_g2p_ByDrug[[drug]]
    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
  }
  else if(dataset == "GDSC" | dataset == "gdsc") {
    use_data <- filter(gdsc_data_g2p_genesfilt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- gdsc_signif_g2p_ByDrug[[drug]]
    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
  }
  else { return("Error: Invalid dataset.") }

@@

```{r, eval=FALSE}
# Drug metadata
drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
colnames(drug_meta) <- c("CID", "Drug")
drug_meta$Drug <- tolower(drug_meta$Drug)
maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
ge_filt <- filter(ge_melt, Hugo_Symbol %in% g2p_genes)

# CCLE
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
ccle_data <- merge(ccle_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
ccle_data$AUC <- as.numeric(ccle_data$AUC)
ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Other", "palegreen3", "springgreen4")
ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3_g2pgenes.rds", compress = "xz")

# CTRP
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
ctrp_data <- merge(ctrp_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Other", "slategray3", "steelblue4")
ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds", compress = "xz")

# GDSC
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
gdsc_data <- merge(gdsc_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Other", "paleturquoise3", "turquoise4")
gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds", compress = "xz")
```

```{r}
ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3_g2pgenes.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
ccle_data_ptmuts$Dataset <- "CCLE"

ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
ctrp_data_ptmuts$Dataset <- "CTRP"

gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
gdsc_data_ptmuts$Dataset <- "GDSC"

@@

# Filter drug screen datasets for G2P genes in drug-gene associations
ccle_data_g2p_genesfilt <- filter(ccle_data_ptmuts, Hugo_Symbol %in% g2p_genes)
ccle_data_g2p_genesfilt$Hugo_Symbol <- ordered(ccle_data_g2p_genesfilt$Hugo_Symbol, levels = g2p_genes)
ctrp_data_g2p_genesfilt <- filter(ctrp_data_ptmuts, Hugo_Symbol %in% g2p_genes)
ctrp_data_g2p_genesfilt$Hugo_Symbol <- ordered(ctrp_data_g2p_genesfilt$Hugo_Symbol, levels = g2p_genes)
gdsc_data_g2p_genesfilt <- filter(gdsc_data_ptmuts, Hugo_Symbol %in% g2p_genes)
gdsc_data_g2p_genesfilt$Hugo_Symbol <- ordered(gdsc_data_g2p_genesfilt$Hugo_Symbol, levels = g2p_genes)
```

@@

### G2P genes and lineage

@@

```{r, eval=FALSE}
ccle_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")

ccle_signif_g2p_ByDrug <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle", grouping_var = "gene")
names(ccle_signif_g2p_ByDrug) <- unique(ccle_data_g2p_genesfilt$Drug)
saveRDS(ccle_signif_g2p_ByDrug, "./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
```

@@

```{r}
ccle_signif_g2p_ByDrug <- readRDS("./data_munging/rds/ccle_signif_g2p_ByDrug.rds")
ccle_signif_g2p_ByDrug_all <- rbindlist(ccle_signif_g2p_ByDrug, use.names = TRUE)
ccle_signif_g2p_ByDrug_all <- ccle_signif_g2p_ByDrug_all[order(ccle_signif_g2p_ByDrug_all$p),]

knitr::kable(ccle_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
ccle_signif_g2p_lineage <- lapply(unique(ccle_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ccle_data_g2p_genesfilt, data_name = "ccle", grouping_var = "lineage")
names(ccle_signif_g2p_lineage) <- unique(ccle_signif_g2p_lineage$Drug)
saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
```

@@

ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "CTRP", grouping_var = "gene")
names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_g2p_genesfilt$Drug)
saveRDS(ctrp_signif_g2p_ByDrug, "./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
```

@@

```{r, eval=FALSE}
ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_g2p_genesfilt$Drug), WilcoxonByDrug, dataset = ctrp_data_g2p_genesfilt, data_name = "ctrp", grouping_var = "lineage")
names(ctrp_signif_g2p_lineage) <- unique(ctrp_signif_g2p_lineage$Drug)
saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
```

@@

## G2P level A gene-drug associations only

>>>>

## Pearson correlation by lineage
```{r}
PearsonByLineage <- function(lin, dataset) {
  use_data <- filter(dataset, group_general_lineage_name == lin)
  use_data <- filter(use_data, !is.na(RPKM))
  use_data_summ <- use_data %>% count(Drug_Gene)
  use_data_summ <- filter(use_data_summ, n >= 3) # cor.test requires at least 3 non-NA data points
  use_data_filt <- filter(use_data, Drug_Gene %in% as.character(unique(use_data_summ$Drug_Gene)))
  if(nrow(use_data_filt) > 0) {
    pearson_res <- use_data_filt %>% group_by(Drug_Gene) %>% summarize(Pearson_Corr = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate, Pearson_Pval = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value)
    pearson_res <- merge(g2p_druggene_p_tally, pearson_res, all.y = TRUE)
    pearson_res$group_general_lineage_name <- lin
    return(pearson_res)
  }
}
```

@@

  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    geom_text(data = g2p_druggenelin_all_summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())

@@

  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = lineage, margin = list(t = 75, l = 75), xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

@@

## Make per-drug boxplots
```{r}
makeDrugBoxplots <- function(drug, dataset) {
  if(dataset == "CCLE" | dataset == "ccle") {
    use_data <- filter(ccle_data_ptmuts, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ccle_signif_g2p_ByDrug[[drug]]
    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
  }
  else if(dataset == "CTRP" | dataset == "ctrp") {
    use_data <- filter(ctrp_data_ptmuts, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ctrp_signif_g2p_ByDrug[[drug]]
    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
  }
  else if(dataset == "GDSC" | dataset == "gdsc") {
    use_data <- filter(gdsc_data_ptmuts, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- gdsc_signif_g2p_ByDrug[[drug]]
    label_text <- data.frame(p.signif = sig$p.signif, p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = g2p_genes)
  }
  else { return("Error: Invalid dataset.") }

@@

```{r, eval=FALSE}
# Drug metadata
drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
colnames(drug_meta) <- c("CID", "Drug")
drug_meta$Drug <- tolower(drug_meta$Drug)
maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
ge_filt <- filter(ge_melt, Hugo_Symbol %in% g2p_genes)
cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)

# CCLE
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "AUC")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Other", ccle_data$Mutation_Status_Nonsilent)
ccle_data <- merge(ccle_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
ccle_data$AUC <- as.numeric(ccle_data$AUC)
ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Other", "palegreen3", "springgreen4")
ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
saveRDS(ccle_data, "./data_munging/rds/ccle_data_18Q3_g2pgenes.rds", compress = "xz")

# CTRP
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Other", ctrp_data$Mutation_Status_Nonsilent)
ctrp_data <- merge(ctrp_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Other", "slategray3", "steelblue4")
ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
saveRDS(ctrp_data, "./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds", compress = "xz")

# GDSC
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Other", gdsc_data$Mutation_Status_Nonsilent)
gdsc_data <- merge(gdsc_data, ge_filt, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"), all.x = TRUE)
gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Other", "paleturquoise3", "turquoise4")
gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
saveRDS(gdsc_data, "./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds", compress = "xz")
```

```{r}
ccle_data <- readRDS("./data_munging/rds/ccle_data_18Q3_g2pgenes.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele_Length == 1 | is.na(ccle_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
ccle_data_ptmuts$Dataset <- "CCLE"
ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)

ctrp_data <- readRDS("./data_munging/rds/ctrp_data_18Q3_g2pgenes.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele_Length == 1 | is.na(ctrp_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
ctrp_data_ptmuts$Dataset <- "CTRP"
ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)

gdsc_data <- readRDS("./data_munging/rds/gdsc_data_18Q3_g2pgenes.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele_Length == 1 | Reference_Allele_Length == 0 | is.na(Reference_Allele_Length))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele_Length == 1 | is.na(gdsc_data_ptmuts$Reference_Allele_Length), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1_Length == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
gdsc_data_ptmuts$Dataset <- "GDSC"
gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)

@@

# Filter drug screen datasets for G2P drugs and genes
ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
```

@@

### Gene

@@

```{r, eval=FALSE}
# G2P drug-gene associations only
ccle_signif_g2p <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Drug_Gene", data = ccle_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
ccle_signif_g2p <- adj_signif(ccle_signif_g2p)
ccle_signif_g2p <- ccle_signif_g2p[order(ccle_signif_g2p$p),]
saveRDS(ccle_signif_g2p, "./data_munging/rds/ccle_signif_g2p_gene.rds")

# Grid comparisons of G2P drugs and genes
ccle_signif_g2p_grid <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ccle_data_g2p_grid, method = "wilcox.test", p.adjust.method = "BH")
ccle_signif_g2p_grid <- adj_signif(ccle_signif_g2p_grid)
ccle_signif_g2p_grid <- ccle_signif_g2p_grid[order(ccle_signif_g2p_grid$p),]
saveRDS(ccle_signif_g2p_grid, "./data_munging/rds/ccle_signif_g2p_grid.rds")
```

@@

```{r}
ccle_signif_g2p_grid <- readRDS("./data_munging/rds/ccle_signif_g2p_grid.rds")

knitr::kable(ccle_signif_g2p_grid[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
ccle_signif_g2p_lineage <- lapply(unique(ccle_data_ptmuts$Drug), WilcoxonByDrug, dataset = ccle_data_ptmuts, data_name = "ccle", grouping_var = "lineage")
names(ccle_signif_g2p_lineage) <- unique(ccle_signif_g2p_lineage$Drug)
saveRDS(ccle_signif_g2p_lineage, "./data_munging/rds/ccle_signif_g2p_lineage.rds")
```

@@

ctrp_signif_g2p_ByDrug <- lapply(unique(ctrp_data_ptmuts$Drug), WilcoxonByDrug, dataset = ctrp_data_ptmuts, data_name = "CTRP", grouping_var = "gene")
names(ctrp_signif_g2p_ByDrug) <- unique(ctrp_data_ptmuts$Drug)
saveRDS(ctrp_signif_g2p_ByDrug, "./data_munging/rds/ctrp_signif_g2p_ByDrug.rds")
```

@@

```{r, eval=FALSE}
ctrp_signif_g2p_lineage <- lapply(unique(ctrp_data_ptmuts$Drug), WilcoxonByDrug, dataset = ctrp_data_ptmuts, data_name = "ctrp", grouping_var = "lineage")
names(ctrp_signif_g2p_lineage) <- unique(ctrp_signif_g2p_lineage$Drug)
saveRDS(ctrp_signif_g2p_lineage, "./data_munging/rds/ctrp_signif_g2p_lineage.rds")
```

@@

## G2P level A drug-gene associations only
